HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ondrej's comments and fixes

\subsection{Annotation Interface.}

@@

HMEANT shares much of HUME's motivation for providing a
measure that decomposes over semantic units, rather than strings, but focuses on verbal
argument structures, ignoring other pervasive phenomena such as nominal predicates, inter-clause
relations and copula clauses.
HUME further diverges from both MEANT and the shallower BLEU and
METEOR measures, in not requiring a reference.
Instead, it compares the source directly with the output
translation. We see this difference as crucial where semantic analysis is concerned, as it
is often impossible to assign a semantic structure to a low quality MT output sentence.
See \secref{sec:hmeant_comp} for a more elaborate discussion of the differences between HUME
and HMEANT.

For instance, consider the sentence ``A coronary angioplasty may not be technically possible'',
which was translated by one of the systems we experimented with as
``Eine koronare Angioplastie kann nicht technisch m{\"o}glich'', i.e., the main verb ``sein'' (``be'') is omitted.
While this may be interpreted is a minor error, HMEANT will assign it a very low score, as it failed to
translate the main verb.

We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess the frequency of some of the major phenomena HMEANT fails to address,
Coppula cluases are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to a conservative estimates that only considers non-auxilliary instances of ``be''.
Nominative argument structures, which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences. Linkers expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified
  non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger.}.
We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, capture the crux of the sentence semantics meanings, and so the coverage of
further phenomena by HUME will first allow to determine empirically
(rather than stipulate), what semantic structures are important
to preserve for MT translation, and which are less important

>>>>

\subsection{Annotation Interface}

@@

HMEANT shares much of HUME's motivation for providing a
measure that decomposes over semantic units, rather than strings. On the other
hand, HMEANT focuses on verbal
argument structures, ignoring other pervasive phenomena such as nominal predicates, inter-clause
relations and copula clauses.
HUME further diverges from both HMEANT (as well as the shallow automatic BLEU and
METEOR measures) in not requiring a reference.
Instead, it compares the source directly with the output
translation. We see this difference as crucial where semantic analysis is concerned, as it
is often impossible to assign a semantic structure to a low quality MT output sentence.

%See \secref{sec:hmeant_comp} for a more elaborate discussion of the differences
%between HUME
%and HMEANT.
% This is here!

For instance, consider the sentence ``A coronary angioplasty may not be technically possible'',
which was translated by one of the systems we experimented with as
``Eine koronare Angioplastie kann nicht technisch m{\"o}glich'', i.e., the main verb ``sein'' (``be'') is omitted.
While this may be interpreted is a minor error, HMEANT will assign it a very low score, as it failed to
translate the main verb. We understand that this is a design feature of HMEANT:
if the translation per se cannot be annotated with verbal argument structure
(for whatever reason, including incomprehensibility), it cannot convey the meaning.
HMEANT thus makes a stricter check of whether the translation can be understood
than we do.

Several experiments with HMEANT applied to languages other than English
\parcite{bojar:wu:ssst:2012,birch-EtAl:2013:WMT,chuchunkov-tarelkin-galinskaya:2014:SSST-8}
indicated that HMEANT does not address some important phenomena.
We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess their frequency: \begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to a conservative estimates that only considers non-auxilliary instances of ``be''.
\item[Nominative argument structures,] which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified
  non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger.}.
\end{inparadesc}

We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, captures the crux of the sentence semantics meanings.
The coverage of
these and other phenomena by HUME will allow to determine empirically
(rather than stipulate), which semantic structures are important
to preserve for MT evaluation, and which are less important.
